Scottish Child Poverty Briefing Plots

### 2024-06-07 minos/outcomes/ChildPovReduction_plots.Rmd
Small fixes for model runs, including some variables that had to be put back after removal, some var type problems fixed, and WIP on a combined relative and absolute poverty intervention

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

@@

@@

summary_group <- 'whole_pop_income_quint'
scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')

@@

# ggplot(base.test, aes(x = year, y = SF_12, group = income_quintile, color = income_quintile)) +
#   geom_smooth(alpha = 0.7) +
#   geom_smooth(data = pov.test, aes(x = year, y = SF_12, group = income_quintile, color = income_quintile), linetype = 'dotted')

ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
  geom_smooth(alpha = 0.7) +
  scale_color_manual(name = "Income Quintile", 
                     values = c("red", "blue", "green", "orange", "purple")) +
  scale_linetype_manual(name = "Scenario", 
                        values = c("Baseline" = "solid", "Intervention" = "dotted")) +
  labs(title = "SF_12 Scores by Income Quintile",
       subtitle = "Comparison of Baseline and Intervention",
       x = "Year",
       y = "Mean SF_12 MCS") +
  theme_minimal() +
  theme(legend.position = "right",
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))

ggplot(data_combined, aes(x = year, y = SF_12, group = scenario, color = scenario)) +
  geom_smooth(alpha = 0.7, aes(linetype = scenario)) +
  facet_wrap(~ income_quintile) +
  scale_color_manual(name = "Scenario", 
                     values = c("Baseline" = "black", "Intervention" = "red")) +
  scale_linetype_manual(name = "Scenario", 
                        values = c("Baseline" = "solid", "Intervention" = "dotted")) +
  labs(title = "SF_12 Scores by Income Quintile",
       subtitle = "Comparison of Baseline and Intervention Scenarios",
       x = "Year",
       y = "SF_12 Score") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))

# Calculate the differences
diff_data <- data %>%
  pivot_wider(names_from = scen, values_from = SF_12) %>%
  mutate(difference = `ChildPovertyReductionRELATIVE_2` - baseline) %>%
  gather(scen, SF_12, baseline, ChildPovertyReductionRELATIVE_2)

ggplot(diff_data, aes(x = year, y = difference, group = income_quintile, color = income_quintile)) +
  geom_line() +
  scale_color_manual(name = "Income Quintile", 
                     values = c("red", "blue", "green", "orange", "purple")) +
  labs(title = "Difference in SF_12 Scores by Income Quintile",
       subtitle = "Intervention Scenario Minus Baseline Scenario",
       x = "Year",
       y = "Difference in SF_12 Score") +
  theme_minimal() +
  theme(legend.position = "right",
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))

# Aggregate data
agg_data <- data %>%
  group_by(year, income_quintile, scen) %>%
  summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
  spread(scen, mean_SF_12) %>%
  mutate(difference = `ChildPovertyReductionRELATIVE_2` - baseline)

ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(name = "Income Quintile", 
                    values = c("red", "blue", "green", "orange", "purple")) +
  labs(title = "Average Difference in SF_12 Scores by Income Quintile",
       subtitle = "Intervention Minus Baseline",
       x = "Year",
       y = "Difference in SF_12 Score") +
  theme_minimal() +
  theme(legend.position = "right",
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))

@@

```{r}
inequality_plots <- function(summary_group, scen.list) {

  #summary_group <- 'whole_pop_income_quint'
  #scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')

  p1 <- ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
    geom_smooth(alpha = 0.7) +
    scale_color_manual(name = "Income Quintile", 
                       values = c("red", "blue", "green", "orange", "purple")) +
    scale_linetype_manual(name = "Scenario", 
                          values = c("Baseline" = "solid", "Intervention" = "dotted")) +
    labs(title = "SF_12 Scores by Income Quintile",
         subtitle = "Comparison of Baseline and Intervention",
         x = "Year",
         y = "Mean SF_12 MCS") +
    theme_minimal() +
    theme(legend.position = "right",
          legend.title = element_text(size = 12),
          legend.text = element_text(size = 10))

  # Aggregate data
  agg_data <- data %>%
    group_by(year, income_quintile, scen) %>%
    summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
    spread(scen, mean_SF_12) %>%
    mutate(difference = `ChildPovertyReductionRELATIVE_2` - baseline)

  p2 <- ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
    geom_bar(stat = "identity", position = "dodge") +
    scale_fill_manual(name = "Income Quintile", 
                      values = c("red", "blue", "green", "orange", "purple")) +
    labs(title = "Average Difference in SF_12 Scores by Income Quintile",
         subtitle = "Intervention Minus Baseline",
         x = "Year",
         y = "Difference in SF_12 Score") +
    theme_minimal() +
    theme(legend.position = "right",
          legend.title = element_text(size = 12),
          legend.text = element_text(size = 10))

```{r}
scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')

inequality_plots(summary_group = 'whole_pop',
                 scen.list = scen.list.test)

>>>>

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old6/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }
  if (summary_group == 'treated') { tit <- 'Treated' }
  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }

@@

# Treated

```{r}
SF12_change_simple(summary_group = 'treated',
                   scen.list = scen.list.test)

SF12_change_percentage(summary_group = 'treated',
                       scen.list = scen.list.test)
```

@@

summary_group <- 'treated'
scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')

@@

@@
